Viscous Erosion in Porous Media

### 2018-03-26 docs/methods/erosion_methods.tex
NM

Next, we aim to measure the opening angle that develops at the front and rear of the body. Since these simulations are actually smooth on a fine scale, a true corner does not exist and we must instead estimate the apparent angle that results from a small region of high curvature. To this end, we first fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region that excludes a small vicinity of the front/rear stagnation points ($\alpha = 0, 0.5$). We then extrapolate the polynomial to the stagnation points which gives an estimate of the angle there. This protocol is subject to some uncertainty, which we will examine further below.

As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry. Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the value $102^\circ$ in the most resolved simulation. This coincides exactly with the valued predicted by our local solutions.

>>>>

Next, we aim to measure the opening angle that develops at the front and rear of the body. Since these simulations are actually smooth on a fine scale, a true corner does not exist and we must instead estimate the apparent angle due to a small region of high curvature. To this end, we first fit the tangent angle $\theta(\alpha)$ with a 7th-degree polynomial over a region excluding the front/rear stagnation points ($\alpha = 0, 0.5$). We then extrapolate the polynomial to the stagnation points, which gives an estimate of the angle there. Although it is subject to some uncertainty (to be examined below), we have found this strategy to give robust angle measurements. In Fig.~\ref{fig:arangle}(b), we show the opening angle on the eroding body for the same three cases of smoothing parameters. The method gives an angle measurement of $180^{\circ}$ for the initially circular geometry, thus providing some confirmation. As time moves forward, erosion carves a sharper corner and the angle decreases monotonically. Here, the effect of the smoothing parameters is more visible, but we still see convergence as $\eps, \sigma \to 0$. In the most accurate simulation (black), the opening angle converges to a value of $102^{\circ}$, which agrees precisely with the analytical prediction from Section \ref{LimitingShape}.

%As seen in Fig.~\ref{fig:arangle}a, the opening angle is initially $180^\circ$, corresponding to the initially circular geometry. Erosion causes the angle to form after a short time, and the angle becomes increasingly sharp as it converges to the value $102^\circ$ in the most resolved simulation. This coincides exactly with the valued predicted by our local solutions.

To examine in more detail the influence of the smoothing parameters, we show in Table

We now examine in detail the influence of the smoothing parameters and the uncertainty in the angle measurements...
